Online Source Code Reuse: A Case Study of Stackoverflow \textit{vs.~}Qualitas OSS

### 2016-08-09 latex/stackoverflow.tex
Updated manual results of individual tools

\subsection{Investigation of extra 100 clone pairs}
In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations classified in . However, only 10 of them appear in the new agreement-based results. Thus, we decided to investigate clone pairs reported by Simian and NiCad without agreement from each other. With our 4 settings, we investigated the largest 25 clone pairs (according to their average SLOC) resulting in 100 more manually investigated pairs. The classification results are shown in Table \ref{tab:classification}.

@@

@@

>>>>

\subsection{Investigation of extra 100 clone pairs}
In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations. However, only 10 of them appear in the new results using tool's agreement. Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement. With our 4 settings, we investigated the largest 25 clone pairs (according to their average SLOC) resulting in 100 more manually investigated pairs. The classification results are shown in Table \ref{tab:classification} and Table \ref{tab:classification_breakdown}.

@@

\begin{table}[H]
	\centering
	\caption{Breakdowns of 100 individual clone pairs}
	\label{tab:classification_breakdown}
	\begin{tabular}{|l|r|r|r|r|r|r|r|}
		\hline 
		Classification & A & B & C & D & E & F & Total \\ 
		\hline 
		Simian$_df$ & 12 & 6 & 1 & 2 & 0 & 4 & 25 \\ 
		\hline
		Simian$_fse13$ & 0 & 0 & 0 & 0 & 0 & 25 & 25 \\
		\hline
		NiCad$_df$ & 0 & 0 & 0 & 11 & 0 & 14 & 25 \\
		\hline
		NiCad$_fse13$ & 0 & 0 & 0 & 5 & 1 & 19 & 25 \\
		\hline
		Total & 12 & 6 & 1 & 18 & 1 & 62 & 100 \\
		\hline
	\end{tabular} 
\end{table}

@@

\newpage
